\hypertarget{privacy-policy}{%
\subsection{Privacy policy}\label{privacy-policy}}

Your data is yours. Whatever you publish unencrypted, is everyones'.

Therefore, it's public information, that cannot be undone. Anyone can
use it to refer to you.

In order to avoid your information go stolen, you should use GPG/PGP
encryption, or whichever other you trust.

Me, Kaotisk Hund, as the internet figure or the real-life caster of this
system, I am responsible for bringing this information and tools to you.

That been said, every user of the algorithm is responsible of how they
use it.

Malicious software, illegal activities, copywriting violations are NOT
welcome. But there is no guarantee that all the users or some of them
will not break this.

Each user has a 5-key identity. Stellar address, IPFS id, SSB id, CJDNS
ip, GPG key. Whatever someone says, it like their fingerprint
everywhere. The reason for this, is to manage a monetizing place
(stellar address) with a filehosting service (IPFS id) with a social
profile (SSB id), a networking address for hosting (CJDNS ip) and an
encryption/signing key (GPG key).

Possibly, someone can generate everything and retry stuff. Or generate
content and try attack the network. Or simply try to make a half thing
to get hands on the funds as it's been proven to be a method of attack
on assets and tokens on other blockchain networks.

I don't know how to prevent that, or what should I do to keep everyone
off the funds. See ASSET\_DISTRIBUTION for more information.
